### 2021-04-09 Chapter-5/Chapter-5.tex
Updates from Overleaf

Accordingly, if Definition~\ref{def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{def}, we can see that the amount of leakages by Definition is a conservative estimation.

@@

\begin{myexample}
Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$, then we count the distribution of  the observation. The process is like traversing a binary tree and increase the counter of the child node. According to Definition~\ref{def}, the amount of the leakage is

>>>>

Accordingly, if Definition~\ref{def} says the vulnerability leakage has $m$ bits of leakages, then the vulnerability can have at least $m$ bits of leakages. We can use the definition to detect those severe leakages. In the examples of Figure~\ref{fig:example1} and Figure~\ref{fig:example2}, because the input secret range from $0$ to $255$, we can calculate the precise value of the amount of information leakage by iterating each input keys. In Figure~\ref{fig:example1}, each item in the array could be read. Therefore, the channel capacity in Figure~\ref{fig:example1} is $\log_2{128} = \,7\, \mathrm{bits}$. In Figure~\ref{fig:example2}, there could be $4$ kinds of information, so the information leakages defined by channel capacity is $\log_2{4} = \,2\, \mathrm{bits}$. Compared with the result from Definition~\ref{chapter5:def}, we can see that the amount of leakages by Definition is a conservative estimation.

@@

\begin{myexample}
Shown in Figure~\ref{fig:design:example2}, we have the following observation from $k_1$ to $k_8$, then we count the distribution of  the observation. The process is like traversing a binary tree and increase the counter of the child node. According to Definition~\ref{chapter5:def}, the amount of the leakage is
